Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-06-01 manuscript.Rmd
wrote score plot function

After visual inspection of the spectra, the chemical differences between modern and fossil polle were explored with a PLSR.
The ordination showed that the fossil pollen are clearly separated from the modern pollen (Fig \@ref(fig:plsrord)).
The regression coefficients reflect our observations from the mean spectra and show high importance of the 1745 lipid peak, the 1500 - 1800 region and the 1170 peak.

>>>>

After visual inspection of the spectra, the chemical differences between modern and fossil pollen were explored with a PLSR model.
The ordination showed that the fossil pollen are clearly separated from the modern pollen (Fig \@ref(fig:plsrord)).
The regression coefficients reflect our observations from the visual inspection and show high importance of the 1745 lipid peak, the 1500 - 1800 region and the 1170 peak (Fig \@ref(fig:plsrcoef)).
